A Simple and Strong Baseline for Universal Targeted Attacks on Siamese Visual Tracking

### 2021-09-08 博士/论文提交/adversarial_attack/TCSVT/大修/正文/main.tex
改caption

\begin{table}[t]
  \centering
  \caption{Overall attack results on OTB-15, GOT-Val and LaSOT.}
  \begin{tabular}{rrccc}
  \toprule
  \multirow{2}{*}[-2pt]{Benchmarks} & \multirow{2}{*}[-2pt]{Metrics} & Clean Videos    & \multicolumn{2}{c}{Perturbed Videos}  \\
  \cmidrule{3-5}
                            &                         & Real Traj. & Real Traj. & Fake Traj.     \\ 
  \midrule
  \multirow{2}{*}{OTB-15} 
  & AO   & 0.642 & 0.063 & 0.759\\
  & Precision & 0.861 & 0.092 & 0.795\\
  \midrule
  \multirow{2}{*}{GOT-Val} 
  & SR & 0.897 & 0.123 & 0.890\\
  & AO & 0.760 & 0.153 & 0.840 \\
  \midrule
  \multirow{3}{*}{LaSOT} 
  & Precision  & 0.514 & 0.046 & 0.605\\
  & Norm. Prec.& 0.551 & 0.048 & 0.702\\
  & AO         & 0.525 & 0.069 & 0.691\\
  %& Succ. rate  & 0.626 & 0.016 & 0.834\\
  \midrule
  \multicolumn{2}{r}{FPS} & 58 & 58 & 58\\
  \bottomrule
  \end{tabular}
  \label{tab:benchmark results}
\end{table}

@@

\begin{table}[t]
  \centering
  \caption{Contribution of each loss on GOT-Val.}
  \begin{tabular}{ccccccc} 
  \toprule
  \multirow{2}{*}[-2pt]{$L_{\text{cls}}$}     & \multirow{2}{*}[-2pt]{$L_{\text{quality}}$} & \multirow{2}{*}[-2pt]{$L_{\text{reg}}$} & \multicolumn{2}{c}{Trageted Attack}          & \multicolumn{2}{c}{Untargeted Attack}           \\ 
  \cmidrule{4-7}
                         &                    &                    & AO                    & SR                    & AO                    & SR                     \\ 
  \midrule
  \checkmark   &    &    & 0.643  & 0.726    & 0.282 & 0.274   \\
     & \checkmark   &    & 0.148  & 0.110    & 0.747 & 0.882   \\
     &    & \checkmark   & 0.726  & 0.762    & 0.243 & 0.238   \\
  \checkmark   & \checkmark   & \checkmark   & 0.840  & 0.890    & 0.153 & 0.123   \\ \bottomrule
  \end{tabular}
  \label{tab:loss}
\end{table}

@@

\begin{table}[t]
  \centering
  \caption{Transferability to different backbones on GOT-Val.}
  \begin{tabular}{rcccccc} 
  \toprule
  \multirow{2}{*}[-2pt]{Backbone} & \multicolumn{2}{c}{Before Attack} & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack}  \\ 
  % \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7}
  \cmidrule{2-7}
                            & AO    & SR                           & AO    & SR                           & AO    & SR                           \\ 
  \midrule
  GoogLeNet                 & 0.760 & 0.897                        & 0.153 & 0.123                        & 0.840 & 0.890                        \\
  AlexNet                   & 0.720 & 0.850                        & 0.496 & 0.577                        & 0.327 & 0.336                        \\
  ShuffleNet                & 0.766 & 0.888                        & 0.496 & 0.557                        & 0.409 & 0.426                       \\
  \bottomrule
  \end{tabular}
  \label{tab:backbone}
\end{table}
\begin{table}[t!]
  \centering
  \caption{Transferability to different tracking architectures on OTB2015.}
  \begin{tabular}{rcccc} 
  \toprule
  \multirow{2}{*}[-2pt]{Trackers} & \multicolumn{2}{c}{Before Attack} & \multicolumn{2}{c}{Untargeted Attack}  \\
  \cmidrule{2-5}
                            & AO & Precision              & AO & Precision                   \\
  \midrule
  SiamRPN++                 & 0.676   & 0.879                  & 0.418   & 0.556                       \\
  SiamRPN                   & 0.666   & 0.876                  & 0.483   & 0.643                       \\
  \bottomrule
  \end{tabular}
  \label{tab:arch}
\end{table}

>>>>

\begin{table}[t]
  \centering
  \caption{Overall attack results on OTB-15, GOT-Val and LaSOT.}
  \begin{tabular}{rrccc}
  \toprule
  \multirow{2}{*}{Benchmarks} & \multirow{2}{*}{Metrics} & Before    & Targeted & Untargeted  \\
                            &                         & Attack & Attack & Attack     \\ 
  \midrule
  \multirow{2}{*}{OTB-15} 
  & AO   & 0.642 & 0.063 & 0.759\\
  & Precision & 0.861 & 0.092 & 0.795\\
  \midrule
  \multirow{2}{*}{GOT-Val} 
  & SR & 0.897 & 0.123 & 0.890\\
  & AO & 0.760 & 0.153 & 0.840 \\
  \midrule
  \multirow{3}{*}{LaSOT} 
  & Precision  & 0.514 & 0.046 & 0.605\\
  & Norm. Prec.& 0.551 & 0.048 & 0.702\\
  & AO         & 0.525 & 0.069 & 0.691\\
  %& Succ. rate  & 0.626 & 0.016 & 0.834\\
  \midrule
  \multicolumn{2}{r}{FPS} & 58 & 58 & 58\\
  \bottomrule
  \end{tabular}
  \label{tab:benchmark results}
\end{table}

@@

\begin{table}[t]
  \centering
  \caption{Analysis of the impact of each loss component on GOT-Val.}
  \begin{tabular}{ccccccc} 
  \toprule
  \multirow{2}{*}[-2pt]{$L_{\text{cls}}$}     & \multirow{2}{*}[-2pt]{$L_{\text{quality}}$} & \multirow{2}{*}[-2pt]{$L_{\text{reg}}$} & \multicolumn{2}{c}{Trageted Attack}          & \multicolumn{2}{c}{Untargeted Attack}           \\ 
  \cmidrule{4-7}
                         &                    &                    & AO                    & SR                    & AO                    & SR                     \\ 
  \midrule
  \checkmark   &    &    & 0.643  & 0.726    & 0.282 & 0.274   \\
     & \checkmark   &    & 0.148  & 0.110    & 0.747 & 0.882   \\
     &    & \checkmark   & 0.726  & 0.762    & 0.243 & 0.238   \\
  \checkmark   & \checkmark   & \checkmark   & 0.840  & 0.890    & 0.153 & 0.123   \\ \bottomrule
  \end{tabular}
  \label{tab:loss}
\end{table}

@@

\begin{table}[t]
  \centering
  \caption{Transferability to different backbones on GOT-Val. The original perturbations are trained on SiamFC++\_GoogleNet, then we directly apply the perturbations to two more different backbones of SiamFC++, \ie, ShuffleNet \cite{ShuffleNet} and AlexNet \cite{AlexNet}.}
  \begin{tabular}{rcccccc} 
  \toprule
  \multirow{2}{*}[-2pt]{Backbone} & \multicolumn{2}{c}{Before Attack} & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack}  \\ 
  % \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7}
  \cmidrule{2-7}
                            & AO    & SR                           & AO    & SR                           & AO    & SR                           \\ 
  \midrule
  GoogLeNet                 & 0.760 & 0.897                        & 0.153 & 0.123                        & 0.840 & 0.890                        \\
  AlexNet                   & 0.720 & 0.850                        & 0.496 & 0.577                        & 0.327 & 0.336                        \\
  ShuffleNet                & 0.766 & 0.888                        & 0.496 & 0.557                        & 0.409 & 0.426                       \\
  \bottomrule
  \end{tabular}
  \label{tab:backbone}
\end{table}
\begin{table}[t!]
  \centering
  \caption{Transferability to different tracking architectures on OTB2015. The original perturbations are trained on SiamFC++\_GoogleNet, then we directly apply the perturbations to two more state-of-the-art anchor-based trackers: AlexNet-based SiamRPN \cite{SiamRPN} and ResNet-based SiamRPN++ \cite{SiamRPN++}.}
  \begin{tabular}{rcccc} 
  \toprule
  \multirow{2}{*}[-2pt]{Trackers} & \multicolumn{2}{c}{Before Attack} & \multicolumn{2}{c}{Untargeted Attack}  \\
  \cmidrule{2-5}
                            & AO & Precision              & AO & Precision                   \\
  \midrule
  SiamRPN++                 & 0.676   & 0.879                  & 0.418   & 0.556                       \\
  SiamRPN                   & 0.666   & 0.876                  & 0.483   & 0.643                       \\
  \bottomrule
  \end{tabular}
  \label{tab:arch}
\end{table}
